Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-15 paper/Paper.tex
We was removed and function 3 times was fixed

\begin{abstract}
This paper describes the first implementation of Decentralized Autonomous Organization (DAO) code to automate organizational governance and decision-making. The code can be used by individuals working together collaboratively outside of a traditional corporate form. It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law. We first discuss the DAO Concept. We then discuss minority rights, and propose a solution to a ``robbing the minority'' attack vector. Finally, we provide a practical implementation of a first generation DAO entity using smart contracts written in Solidity on the Ethereum blockchain.
\end{abstract}

@@

We present a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality. We illustrate a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2) where governance rules are formalized, automated and enforced using software. Specifically, we have written generic smart contract code (\cite{szabo1997formalizing, miller1997future}) that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. In this paper we explain how a DAO's code works. We do so by focusing on some basic formation and governance features, including formation, creation and voting rights.

We first describe a DAO's formation and basic functionality. We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split.'' We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split.''

@@

A word of caution, at the outset:  the legal status of DAOs remains the subject of active and vigorous debate and discussion. Not everyone shares the same definition. Some have said that they are autonomous code and can operate independently of legal systems; others have said that they must be owned or operate by humans or human created entities. There will be many uses cases, and the DAO code will develop over time. Ultimately, how a DAO functions and its legal status will depend on many factors, including how DAO code is used, where it is used, and who uses it. We do not speculate about the legal status of DAOs worldwide. This paper is not intended to offer legal advice or conclusions. Anyone who uses DAO code will do so at their own risk.

@@

A DAO stores ether and other Ethereum based tokens and transmits them based on the DAO's code. It does not do much else. It cannot build a product, write code or develop hardware. It requires what we have called a ``Contractor'' to accomplish these and other goals. A DAO selects a Contractor by accepting a Contractor's proposal.

@@

\section{Notation}
Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. This is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit. We define this as $10^{-16}$ DAO token.
\section{Majority robs minority attack}
Minority owner rights can be a problem in any corporate form. Minority rights may be protected or addressed by provisions in corporate governance documents or by statute or judge-made law. But many of these solutions fail because minority owners may lack voting rights or the ability to ``vote with their feet" and easily retrieve their capital. We present a solution to this problem in the DAO's code.

@@

\section{Token Price} \label{TokenPrice}
DAO Token Creation schedule increases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO. 
For the DAO described here, we have chosen the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
This results in a constant Creation ratio in the beginning, until $2$ weeks before the end of the DAO Creation. At this time the Creation ratio increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation ratio of $1.5 \: \Xi_c$ per base unit of DAO token.

@@

\section{Contracts}
This section will detail the smart contracts implementing the aforementioned concept. The contracts are written in the programming language Solidity (\cite{ReitwiessnerWoodSolidity}).
Each contract has member variables and functions which can be externally called by sending a transaction to the Ethereum network with the DAO contract address as the recipient and the method ID (optional with parameters) as data. In this section we will discuss the meaning of the variables and the functions in detail.

@@

\end{verbatim}
\begin{multicols}{2}
The original contract used as a starting point for the ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
\url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
Now we will define the member variables and functions one at a time.

@@

We will now discuss the functions of the DAO contract in detail. Many of the member variables that are used in this contract are defined in one of the other three contracts.

@@

In this section we give a description of how reward tokens are implemented in this contract. Much of the information has already been explained, but it is restated here for clarity.

@@

In this section we want to formally describe some parameters and their behavior during a split.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the address of the new contract as parameter.
If accepted, the complete DAO moves to the new contract, meaining, all ether and reward tokens are transferred to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens.
Another option is to create new tokens in the new contract based on the token distribution in the old contract. This can also be achieved by a proof that the old tokens are destroyed (sending to the $0$ address).
This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.

>>>>

\begin{abstract}
This paper describes the first implementation of Decentralized Autonomous Organization (DAO) code to automate organizational governance and decision-making. The code can be used by individuals working together collaboratively outside of a traditional corporate form. It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law. First the DAO Concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector isproposed. Finally, a practical implementation of a first generation DAO entity is provided using smart contracts written in Solidity on the Ethereum blockchain.
\end{abstract}

@@

This paper presents a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality. This paper illustrates a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2)  governance rules are formalized, automated and enforced using software. Specifically, generic smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. This paper explains how a DAO's code works, focusing on some basic formation and governance features, including structure, creation and voting rights.

First a DAO's Creation Phase and basic functionality are described. Then minority owner rights are discussed and a solution to the ``Majority Robbing the Minority Attack'' problem is proposed: the ``DAO split.'' The smart contract code is then explored in detail, and conclude with an explanation and detailed specification of the ``DAO split.''

@@

A word of caution, at the outset:  the legal status of DAOs remains the subject of active and vigorous debate and discussion. Not everyone shares the same definition. Some have said that they are autonomous code and can operate independently of legal systems; others have said that they must be owned or operate by humans or human created entities. There will be many uses cases, and the DAO code will develop over time. Ultimately, how a DAO functions and its legal status will depend on many factors, including how DAO code is used, where it is used, and who uses it. This paper does not speculate about the legal status of DAOs worldwide. This paper is not intended to offer legal advice or conclusions. Anyone who uses DAO code will do so at their own risk.

@@

A DAO stores ether and other Ethereum based tokens and transmits them based on the DAO's code. It does not do much else. It cannot build a product, write code or develop hardware. It requires a ``Contractor'' to accomplish these and other goals. A DAO selects a Contractor by accepting a Contractor's proposal.

@@

\section{Notation}
Throughout this paper, $\Xi$ always represents an amount of ether in its base unit wei. This is defined as $1 \: \text{Wei} = 10^{-18} \: \text{Ether}$ (\cite{Wood2014ethereum}).
Similarly, DAO tokens are denoted with $T$ and always represent the amount of DAO tokens in its base unit, defined as $10^{-16}$ DAO token.

\section{Majority robs minority attack}
Minority owner rights can be a problem in any corporate form. Minority rights may be protected or addressed by provisions in corporate governance documents or by statute or judge-made law. But many of these solutions fail because minority owners may lack voting rights or the ability to ``vote with their feet" and easily retrieve their capital. This paper presents a solution to this problem in the DAO's code.

@@

\section{Token Price} \label{TokenPrice}
DAO Token Creation schedule increases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO. 
The DAO described in this paper has the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
This results in a constant Creation ratio in the beginning, until $2$ weeks before the end of the DAO Creation. At this time the Creation ratio increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation ratio of $1.5 \: \Xi_c$ per base unit of DAO token.

@@

\section{Contracts}
This section will detail the smart contracts implementing the aforementioned concept. The contracts are written in the programming language Solidity (\cite{ReitwiessnerWoodSolidity}).
Each contract has member variables and functions which can be externally called by sending a transaction to the Ethereum network with the DAO contract address as the recipient and the method ID (optional with parameters) as data. This section will discuss the meaning of the variables and the functions in detail.

@@

\end{verbatim}
\begin{multicols}{2}
The original contract used as a starting point for the ‘’DAO’’ was: \url{http://chriseth.github.io/browser-solidity/?gist=192371538cf5e43e6dab} as described in 
\url{https://blog.ethereum.org/2015/12/04}. The main feature added is the splitting mechanism and all that comes with it.
This section will define the member variables and functions from the above smart contract one at a time.

@@

This section will discuss the functions of the DAO contract in detail. Many of the member variables that are used in this contract are defined in one of the other three contracts.

@@

This section gives a description of how reward tokens are implemented in this contract. Much of the information has already been explained, but it is restated here for clarity.

@@

This section formally describes a few important parameters and their behavior during a split.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the address of the new contract as parameter.
If accepted, the complete DAO moves to the new contract, meaning, all ether and reward tokens are transferred to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens.
Another option is to create new tokens in the new contract based on the token distribution in the old contract. This can also be achieved by a proof that the old tokens are destroyed (sending to the $0$ address).
This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.
